---
title: "Lessons learned: creating tutorials teaching Agent-Based Modelling for Archaeologists"
author:
  - name: Ronald M. Visser
    orcid: 0000-0001-6966-1729
    affil-id: 1
  - name: Annemarie Jutte
    orcid: 
    affil-id: 1
  - name: Doug Rocks-Macqueen 
    orcid: 
    affil-id: 2
  - name: Iza Romanowska 
    orcid: 
    affil-id: 3
  - name: Tom Brughmans
    orcid: 
    affil-id: 3
  - name: Laura van der Knaap 
    orcid: 
    affil-id: 4
  - name: Karsten Lambers 
    orcid: 
    affil-id: 4
  - name: Kenneth Aitchison 
    orcid: 
    affil-id: 2
affiliations:
  - id: 1
    name: Saxion University of Applied Sciences.
  - id: 2
    name: Landward Research Teoranta.
  - id: 3
    name: Aarhus University.
  - id: 4
    name: Leiden University.
date: "`r format(Sys.time(), '%d %B %Y')`"
geometry:
  - margin=1in
output:
  bookdown::pdf_document2:
    number_sections: yes
    keep_tex: true
    fig_caption: yes
  html_document:
    number_sections: yes
    fig_caption: yes
  word_document:
    number_sections: yes
bibliography: references.bib
csl: journal-of-computer-applications-in-archaeology.csl
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(forcats)
```

# Introduction

ABM application increased in Archaeology

No formal training

EU project

# Method

During the project we have developed tutorials. The tutorials were first designed using storyboards which were later converted into tutorials using NetLOGO Web (<https://www.netlogoweb.org/launch>) and Javascript (). The tutorials were developed together and we worked together using GitHub (<https://github.com/lljvdk/EU-ABMA/>). During the project initial testing was done with all authors and issues in GitHub were used to tackle bugs.

The tutorial were tested during various online and in-person conferences. In addition, we also had students working with the tutorials at Saxion Universty of applied sciences and Leiden University. We used the feedback of the participants to improve the tutorials. The feedback was obtained structurally using two surveys using Qualtrics. The participants of the events were asked to answer questions of a survey before participating. We used the answers to understand what the background of the participants was and to get an estimate of their level of knowledge in relation to ABM (see appendix ... for the questions). After the participants worked with the tutorials during the event they were asked to answer a second survey. Questions of this survey were aimed at the measuring the effectiveness of the tutorials and getting feedback on the workshop and tutorials (see appendix ... for the questions). For some events participants had to register beforehand and we were able to send the pre-workshop survey by email. At other events no registration was possible or necessary and the pre-workshop survey was given at the start of the event. The post-workshop survey was distributed using QR-codes or links at the end of the workshop during the event. After each event we have improved the tutorials based on the received feedback.

| Conference or event          | Period                  | Online, in person or hybrid | Number of participants | Number of registrations |
|---------------|---------------|---------------|---------------|---------------|
| CAA Amsterdam                | April 2023              | In person                   |                        |                         |
| EAA Belfast                  | August 2023             | In person                   |                        | No registration         |
| CAA-DE/NL-Fl Online workshop | October 2023            | Online                      |                        |                         |
| Reuvensdagen                 | November 2023           | In person                   |                        | No registration         |
| CAA-UK                       | November 2023           | Hybrid                      |                        |                         |
| Leiden (course)              | December 2023           | In person                   |                        |                         |
| Aarhus                       | January/February 2024   | Online                      | 178                    | 400                     |
| Saxion                       | March 2023-January 2024 | In person                   | 18                     |                         |

: Conferences, events and situations were the workshops given and the tutorials were tested.

The surveys were analysed using R [@rcoreteam2023]. The following packages were used for analyses: ggplot2 [@wickham2016], dplyr [@wickham2023a], tidyr [@wickham2023], forcats[@wickham2023b], lubridate [@grolemund2011] and stringr [@wickham2023c]. The date and the code is available at <https://github.com/RonaldVisser/ABM_tutorials> and (... insert Zenodo reference...)

# Results

## Tutorials

## Before tutorial

A large proportion of the participants of the workshops gave us information using the survey before the workshops 172 of (...total number...) participants. The respondents came from many different countries all over the world (see Figure \@ref(fig:nationality). The number of female respondents slightly outnumber the male ones and a small group did not share their gender and two were non-binary (see Figure \@ref(fig:gender-age)). The ages of the respondents ranged from below 20 to over 70, reaching people in different age classes, although the majority was aged between 20 and 40. It seems that the different events also had a slightly different distribution of both gender and age. For example, more older people attended the workshop at the CAA conference in April 2023 and more male people were present during the workshop at the Reuvensdagen in November 2023.

students???

```{r nationality, fig.cap="The nationality of the participants that filled in the survey.", echo=FALSE}
pre_surveys <- readRDS("data/pre_workshop_surveys.rds")
ggplot(pre_surveys, aes(x = `What.is.you.nationality....Nationality...Text`)) +
  geom_bar() +  coord_flip() + xlab("Nationality")

```

```{r gender-age, fig.cap="The gender and age of the respondents for each workshop", echo=FALSE}
ggplot(pre_surveys, aes(x = `What.is.your.age.`, fill = `What.is.your.gender....Selected.Choice`)) +
  geom_bar() + labs(x= "Age", y="Count", fill = "Gender") + facet_grid(~Workshop) +   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```

Most of the respondents had several skills with computer applications in archaeology (see Figure \@ref(fig:computer-skills)), and many of them did have some knowledge of ABM, although a large group was completely new to the subject. The majority had never applied ABM before participating in the workshops with 14 having applied ABM. It is interesting to note that many respondents did know what kind of software was available for ABM (see Figure \@ref(fig:abm-knowledge)).

```{r, computer-skills, fig.cap="The computer skills of the respondents.", out.width="50%"}
pre_surveys %>%
  select(`Which.computer.skills.do.you.have....Selected.Choice`) %>%
  separate_rows(`Which.computer.skills.do.you.have....Selected.Choice`, sep = ',\\s*') %>%
  filter(`Which.computer.skills.do.you.have....Selected.Choice`!="") %>%
  group_by(`Which.computer.skills.do.you.have....Selected.Choice`) %>%
  ggplot(aes(x=`Which.computer.skills.do.you.have....Selected.Choice`)) + geom_bar() +
    xlab("Computer skills") + coord_flip()
```

```{r, abm-knowledge, fig.cap="Respondents knowledge and experience with ABM.", fig.show="hold", out.width="50%"}
pre_surveys %>% 
  filter(`Do.you.know.what.Agent.Based.Modeling.is.`!="Not shared") %>% 
  ggplot(aes(x = `Do.you.know.what.Agent.Based.Modeling.is.`)) +
    geom_bar(na.rm = TRUE) + xlab("I know what ABM is") + facet_grid(~Workshop)
pre_surveys %>%
  select(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`) %>%
  filter(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`!="") %>%
  separate_rows(Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice, sep = ',\\s*') %>%
  group_by(`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`) %>%
  ggplot(aes(x=`Which.software.do.you.know.for.Agent.Based.Modeling....Selected.Choice`)) + geom_bar() +
  xlab("ABM Software known") + coord_flip()
```

## After tutorial

## Final tutorials

## Dissemination of tutorials

Website

# Conclusion

Lessons learned

Future aspects

# Acknowledgements

The roles of this paper according to CReDiT (Contributor Roles Taxonomy):

Kenneth Aitchison

Tom Brughmans

Annemarie Jutte

Laura van der Knaap

Karsten Lambers

Doug Rocks-Macqueen (Software)

Iza Romanowska

Ronald M. Visser (Writing -- original draft, Formal Analysis, Visualization)

# References
